Check Coverage

### 2019-10-08 analysis/merge_data.Rmd
Drop species without trait data from biotime_data.

biotime_traits <- comp_biotime_traits %>%
  filter(study_id %in% inc_coverage$study_id)
```

@@

@@

Format tables
```{r}
fd_table <- fd %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  View()

study_table <- biotime_data %>%
  group_by(study_id) %>%
  mutate(min_year = min(year), max_year = max(year)) %>% 
  #select(study_id, plot, taxa, latitude, longitude, min_year, max_year) %>%
  select(study_id, taxa, min_year, max_year) %>%
  distinct() %>%
  left_join(coverage, by = "study_id")
```

>>>>

biotime_traits <- comp_biotime_traits %>%
  filter(study_id %in% inc_coverage$study_id, !is.na(sourceName))
```

@@

Create table of info for each study
```{r}
study_table <- biotime_data %>%
  group_by(study_id) %>%
  mutate(min_year = min(year), max_year = max(year)) %>% 
  #select(study_id, plot, taxa, latitude, longitude, min_year, max_year) %>%
  select(study_id, taxa, min_year, max_year) %>%
  distinct() %>%
  left_join(coverage %>% select(study_id, coverage = perc), by = "study_id")

usethis::use_data(study_table)
```

@@

Format tables
```{r}
fd_table <- fd %>% 
  select(year, study_id, plot, richness = nbsp, everything(), -sing.sp) %>%
  gather(metric, value, contains("F"), RaoQ) %>%
  View()
```
